### 2018-08-08 Sections/QTCP_protocol_stack.tex
floats
Finito index

\begin{figure}[!htb]\index{QTCP protocol stack}
\includegraphics[width=0.47\textwidth]{stack}
\caption{Protocol stack for QTCP. The protocol stack mediates communication of quantum data from Alice to Bob using the shown layers of abstraction. The end goal is to provide Bob a virtual interface to Alice's transmitted data, while remaining oblivious to the underlying protocol.} \label{fig:stack}\index{QTCP protocol stack}
\end{figure}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Transport(Packet):
\begin{enumerate}
    \item nextNode = Packet.RoutingQueue.Pop()
    \item Packet.PhysicallySendTo(nextNode)
    \item Packet.WaitUntilArrivesAt(nextNode)
    \item checksum = Hash(Packet.Header + Packet.ClassicalData)
    \item if(checksum $\neq$ Packet.Header.Checksum) \{
    \setlength{\itemindent}{0.2in}
    \item Packet.Sender.Notify(\textsc{Failure})
    \item Packet.Recipient.Notify(\textsc{Failure})
    \item Packet.Discard()
    \item $\Box$
        \setlength{\itemindent}{0in}
\item \}
    \item Packet.Costs += IncomingLink.Costs
    \item Packet.Attributes.Update()
    \item if(Packet.RoutingQueue.Length = 0) \{
    \setlength{\itemindent}{0.2in}
    \item Return(Packet)
        \setlength{\itemindent}{0in}
    \item \}
    \setlength{\itemindent}{0in}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{Algorithm implemented by the \textsc{Transport} layer of QTCP for each \textsc{Packet}. The \texttt{Attributes.Update()} function is left undefined. This is where arbitrary \textsc{Attribute} dynamics may take place.} \label{alg:transport_alg}
\end{table}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Reconstruction(Packets):
\begin{enumerate}
    \item Packets.WaitUntilAllReceived()
    \item message = Packets.SortByOrderAscending().data
    \item Packets.Receiver.Notify(message)
     \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{The goal of the \textsc{Reconstruction} layer, is to take a collection of received \textsc{Packets} and reassemble them into the \textsc{Message}.} \label{alg:reconstruction}
\end{table}

@@

\subsubsection{Quality of service} \label{sec:QOS} \index{Quality of service layer}

@@

As an alternative to checksums, we could borrow the notion of quantum error correction (QEC)\index{Quantum error correction (QEC)} and fault-tolerance from quantum computing theory \cite{???}. Here we encode a quantum state into a (polynomially) larger Hilbert space. \textit{Syndrome measurements}\index{Syndrome measurements} on some of the states in this larger space allow us to both detect and correct universal error models, such as depolarisation or dephasing, provided that error rates are within the fault-tolerance threshold of the code being employed.

>>>>

\begin{figure}[htpb]\index{QTCP protocol stack}
\includegraphics[width=0.47\textwidth]{stack}
\caption{Protocol stack for QTCP. The protocol stack mediates communication of quantum data from Alice to Bob using the shown layers of abstraction. The end goal is to provide Bob a virtual interface to Alice's transmitted data, while remaining oblivious to the underlying protocol.} \label{fig:stack}\index{QTCP protocol stack}
\end{figure}

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Transport(Packet):
\begin{enumerate}
    \item nextNode = Packet.RoutingQueue.Pop()
    \item Packet.PhysicallySendTo(nextNode)
    \item Packet.WaitUntilArrivesAt(nextNode)
    \item checksum = Hash(Packet.Header + Packet.ClassicalData)
    \item if(checksum $\neq$ Packet.Header.Checksum) \{
    \setlength{\itemindent}{0.2in}
    \item Packet.Sender.Notify(\textsc{Failure})
    \item Packet.Recipient.Notify(\textsc{Failure})
    \item Packet.Discard()
    \item $\Box$
        \setlength{\itemindent}{0in}
\item \}
    \item Packet.Costs += IncomingLink.Costs
    \item Packet.Attributes.Update()
    \item if(Packet.RoutingQueue.Length = 0) \{
    \setlength{\itemindent}{0.2in}
    \item Return(Packet)
        \setlength{\itemindent}{0in}
    \item \}
    \setlength{\itemindent}{0in}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{Algorithm implemented by the \textsc{Transport} layer of QTCP for each \textsc{Packet}. The \texttt{Attributes.Update()} function is left undefined. This is where arbitrary \textsc{Attribute} dynamics may take place.} \label{alg:transport_alg}
\end{table}

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Reconstruction(Packets):
\begin{enumerate}
    \item Packets.WaitUntilAllReceived()
    \item message = Packets.SortByOrderAscending().data
    \item Packets.Receiver.Notify(message)
     \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{The goal of the \textsc{Reconstruction} layer, is to take a collection of received \textsc{Packets} and reassemble them into the \textsc{Message}.} \label{alg:reconstruction}
\end{table}

@@

\subsubsection{Quality of service} \label{sec:QOS} \index{Quality of service (QoS) layer}

@@

As an alternative to checksums, we could borrow the notion of quantum error correction (QEC)\index{Quantum error correction (QEC)} and fault-tolerance\index{Fault-tolerance} from quantum computing theory \cite{???}. Here we encode a quantum state into a (polynomially) larger Hilbert space. \textit{Syndrome measurements}\index{Syndrome measurements} on some of the states in this larger space allow us to both detect and correct universal error models, such as depolarisation or dephasing, provided that error rates are within the fault-tolerance threshold of the code being employed.

### 2018-08-08 Sections/classical_networking_protocols.tex
Finito index

\subsubsection{User Datagram Protocol} \index{User Datagram Protocol}

@@

Key examples for the use of UDP are realtime audio and video transmission. If a packet associated with a frame in a video link is delayed and arrives several frames late, it is useless, since it is associated strictly with a previous frame in the video that has already passed. Quality control, in the form of contacting the sender to request a retransmission, would therefore achieve nothing. This applies similarly to live audio streaming, such as voice over IP (VoIP)\index{Voice over IP}, where the late arrival of a packet cannot possibly be correctly inserted into the audio playback and might as well be discarded.

@@

\subsubsection{Transmission Control Protocol} \label{sec:TCP} \index{Transmission Control Protocol}

>>>>

\subsubsection{User Datagram Protocol} \index{User Datagram Protocol (UDP)}

@@

Key examples for the use of UDP are realtime audio and video transmission. If a packet associated with a frame in a video link is delayed and arrives several frames late, it is useless, since it is associated strictly with a previous frame in the video that has already passed. Quality control, in the form of contacting the sender to request a retransmission, would therefore achieve nothing. This applies similarly to live audio streaming, such as voice over IP (VoIP)\index{Voice over IP (VoIP)}, where the late arrival of a packet cannot possibly be correctly inserted into the audio playback and might as well be discarded.

@@

\subsubsection{Transmission Control Protocol} \label{sec:TCP} \index{Transmission Control Protocol/Internet Protocol (TCP/IP)}

### 2018-08-08 Sections/cloud_quantum_computing.tex
Indexing
Finito index

\subsubsection{Distributed unitary error averaging}\index{Unitary error averaging}\index{Distributed unitary error averaging}

@@

The cluster state (Sec.~\ref{sec:CSQC})\index{Cluster states}, topological code (Sec.~\ref{sec:topol_codes})\index{Topological codes} and quantum random walk (Sec.~\ref{sec:QW})\index{Quantum random walk} models for quantum computation may find themselves to be particularly well-suited to distributed implementation, since they naturally reside on graphs, whose nodes needn't be held locally by a single user, but could instead be shared across multiple hosts with the ability for graph nodes to intercommunicate. Then only classical communication is required to complete a computation will quantum information not localised to any particular node.

@@

The availability of a globe-spanning quantum network on satellites brings the opportunity for fundamental quantum mechanical experiments and unprecedented length scales and velocities in the future. Satellite-to-satellite\index{Satellite-to-satellite} photon transfer can allow for ultra-long distance quantum communications that are not possible on Earth due to atmospheric loss. Another unique aspect of space is that satellites move at high velocities -- typically at $10^{-5} $ times the speed of light\index{Speed of light} for LEO satellites. The combination of both of these effects gives a unique opportunity for performing relativistic quantum information\index{Relativistic quantum information} experiments to test fundamental physics.

>>>>

\subsubsection{Distributed unitary error averaging}\index{Unitary error averaging}\index{Distributed unitary error averaging}\label{sec:error_av_parallel}

@@

The cluster state (Sec.~\ref{sec:CSQC})\index{Cluster states}, topological code (Sec.~\ref{sec:topol_codes})\index{Topological codes} and quantum random walk (Sec.~\ref{sec:QW})\index{Quantum random walks} models for quantum computation may find themselves to be particularly well-suited to distributed implementation, since they naturally reside on graphs, whose nodes needn't be held locally by a single user, but could instead be shared across multiple hosts with the ability for graph nodes to intercommunicate. Then only classical communication is required to complete a computation will quantum information not localised to any particular node.

@@

The availability of a globe-spanning quantum network on satellites brings the opportunity for fundamental quantum mechanical experiments and unprecedented length scales and velocities in the future. Satellite-to-satellite\index{Satellite-to-satellite communication} photon transfer can allow for ultra-long distance quantum communications that are not possible on Earth due to atmospheric loss. Another unique aspect of space is that satellites move at high velocities -- typically at $10^{-5} $ times the speed of light\index{Speed of light} for LEO satellites. The combination of both of these effects gives a unique opportunity for performing relativistic quantum information\index{Relativistic quantum information} experiments to test fundamental physics.

### 2018-08-08 Sections/cryptowars.tex
Finito index

Private- (or symmetric-) key cryptography is perhaps the most basic (and useful) cryptographic primitive, enabling encryption of a channel between two parties who share a secret key\index{Secret key} -- a random bit-string of length determined by the encryption algorithm. The same secret key is employed for both encryption and decryption operations, making it of utmost importance that it be retained secret.

@@

\subsection{One-time pad cipher}\index{One-time pad cipher}

There is one and only one \textit{provably} secure (in the sense of information-theoretic security\index{Information-theoretic security} as opposed to computational security\index{Computational security}) encryption protocol -- the \textit{one-time pad}\index{One-time pad cipher}. This protocol requires Alice and Bob to share a random secret key as long as the message (plaintext\index{Plaintext}) being communicated between them. The two bit-strings undergo bit-wise XOR operations to form the ciphertext\index{Ciphertext}. Mathematically,\index{One-time pad cipher}
\begin{align}
c = s \oplus k,
\end{align}
where $\oplus$ is the bitwise XOR operation (equivalently addition modulo 2), and $c$, $s$ and $k$ are the ciphertext, plaintext and key bit-strings respectively, all of which are of the same length,
\begin{align}
	|c|=|s|=|k|.
\end{align}

@@

Importantly, the secrecy of the one-time pad\index{One-time pad cipher} strictly requires that a key never be reused. A fresh key must be generated for each message sent, otherwise trivial frequency analysis\index{Frequency analysis} techniques can be employed to compromise security. If the same key $k$ is used to encode two messages $s_1$ and $s_2$, yielding ciphertexts,
\begin{align}
c_1&=s_1\oplus k,\nonumber\\
c_2&=s_2\oplus k,
\end{align}
then we trivially obtain,
\begin{align}
c_1 \oplus c_2 &= (s_1 \oplus k) \oplus (s_2 \oplus k) \nonumber \\
&= (s_1 \oplus s_2) \oplus (k \oplus k) \nonumber \\
&= s_1 \oplus s_2,
\end{align}
which is independent of the key. Now a frequency analysis on the bitwise XOR of two plaintexts can be applied, without requiring any knowledge of the key whatsoever.

@@

RSA \cite{bib:RSA} was the first published public-key cryptographic protocol, and forms the backbone for most encryption used on the internet today. It achieves its security based on the belief that factorising large integers into constituent primes is a computationally hard problem -- a so-called `trapdoor function'\index{Trapdoor function}. The algorithm is built upon number theory using modular arithmetic, described in detail in Alg.~\ref{alg:RSA}.

@@

In the case of RSA encryption, whose security derives from the believed computational hardness of factorising large numbers, the most efficient known classical algorithm for integer factorisation is the general number field sieve (GNFS)\index{General number field sieve}, with time-complexity,
\begin{align} \label{eq:GNFS_scaling}
	O(\mathrm{exp}[O(1) (\log n)^{\frac{1}{3}} (\log\log n)^{\frac{2}{3}}]),
\end{align}
which scales poorly for large $n$, keeping in mind that present-day implementations of RSA accommodate key lengths of up to 4,096 bits, as for example is implemented by the Pretty Good Privacy (PGP)\index{Pretty Good Privacy} package.

@@

Note that when performing a brute-force attack against a private encryption key\index{Private-key encryption}, a quadratic speedup effectively halves the key length in terms of algorithmic runtime, since \mbox{$O(\sqrt{2^k}) = O(2^{k/2})$}. Thus, in the quantum era private key lengths will need to be doubled to maintain the same security against brute-force attacks.

@@

Hashing does not have any known quantum algorithm with exponential improvement, however using a Grover search\index{Grover's algorithm} one can achieve a quadratic speedup, using the same idea as for enhancing \textbf{NP}-complete problems by treating the hash function as a search oracle\index{Oracle}. This however does not pose a fundamental security concern as it will speed up the Bitcoin mining process, but does not circumvent the upper-bound on the number of coins that may be in existence. Already classical mining has pushed the Bitcoin money supply close to its asymptotic maximum and there is limited room for additional mining\footnote{Bitcoin mining has gained so much traction and become so competitive that desktop PCs have become uneconomical for mining. Instead miners are resorting to utilising specialised hardware in the form of CUDA cores\index{CUDA cores}, FPGAs\index{FPGA} and ASICs\index{ASIC} (or by secretly using the company supercomputer while the boss isn't looking).}.

@@

Thankfully, there are two saving graces. First of all, much research is being carried out into \textit{post-quantum classical cryptography}\index{Post-quantum classical cryptography}. That is, public-key cryptosystems based upon trapdoor functions\index{Trapdoor function} that reside outside of \textbf{BQP} and are therefore not efficiently attacked by quantum computers. One such line of research is to construct cryptosystems based upon \textbf{NP}-complete problems, such as the McEliece protocol\index{McEliece protocol}. Recall from Fig.~\ref{fig:complexity_classes} that \textbf{NP}-complete is strongly believed to reside completely outside of \textbf{BQP}. However, while many computer scientists might be comfortable with such a level of security, it is nonetheless based on the unproven conjecture that \textbf{NP}-complete and \textbf{BQP} do not intersect, i.e \mbox{$\mathbf{NP}\nsubseteq\mathbf{BQP}$}. What would be much more satisfying would be protocols demonstrating information-theoretic security\index{Information-theoretic security} rather than computational security\index{Computational security}. Here quantum mechanics can help us -- \textit{quantum cryptography}.

@@

\subsection{Quantum key distribution} \label{sec:QKD} \index{Quantum key distribution}

@@

Quantum key distribution (QKD) protocols facilitate shared, secret randomness, where any intercept-resend\index{Intercept-resend attack} (or man-in-the-middle attack) attack may be detected and rejected, guaranteed by the laws of quantum physics (specifically the Heisenberg uncertainty principle\index{Heisenberg uncertainty principle} and no-cloning theorem\index{No-cloning theorem}). This shared, secret randomness may subsequently be employed in a one-time pad cipher\index{One-time pad cipher}, presenting us with true information-theoretic security\index{Information-theoretic security}.

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function BB84():
\begin{enumerate}
\item Alice chooses a random bit, $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{BB84\index{BB84 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string for use in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:bb84}
\end{table}

@@

To understand the secrecy of the protocol as described in Alg.~\ref{alg:bb84}, suppose an eavesdropper, Eve, were to perform an intercept-resend\index{Intercept-resend attack} attack on the channel between Alice and Bob. At that stage in the protocol Alice had not yet announced her choice of encoding bases, and Eve will not know the bases in which to measure states without randomly collapsing them onto values inconsistent with Alice's encoding. Thus, by sacrificing some of their shared bits, via openly communicating them to one another for comparison, such an attack will be detected with asymptotically high security. Now Alice and Bob have great confidence that they have a shared, secret, random bit-string, which may subsequently be employed in a one-time pad\index{One-time pad cipher} with perfect secrecy.

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function E91():
\begin{enumerate}
\item A central server shares a Bell pair between Alice and Bob,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
\item Alice randomly measures her qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Bob randomly measures his qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Alice and Bob share what their measurement bases were (classically and unencrypted).
\item When Alice and Bob's bases were consistent they store the measurement outcomes as a shared random bit.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{E91\index{E91 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photonic Bell pairs. Upon completion of the protocol, Alice and Bob share a random bit-string of ruse in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:e91}
\end{table}

@@

Like quantum computing, QKD protocols may be adapted to the CV domain also. Alg.~\ref{alg:cv_qkd} describes a simple such scheme based on encoding in phase-space\index{Phase-space}, where the basis states are coherent states of different amplitudes and phases. The goal is the same as BB84 -- to securely share a random bit-string for use in a one-time-pad\index{One-time-pad}.

>>>>

Private- (or symmetric-) key cryptography is perhaps the most basic (and useful) cryptographic primitive, enabling encryption of a channel between two parties who share a secret key\index{Private key} -- a random bit-string of length determined by the encryption algorithm. The same secret key is employed for both encryption and decryption operations, making it of utmost importance that it be retained secret.

@@

\subsection{One-time pad cipher}\index{One-time pad}

There is one and only one \textit{provably} secure (in the sense of information-theoretic security\index{Information-theoretic security} as opposed to computational security\index{Computational security}) encryption protocol -- the \textit{one-time pad}\index{One-time pad}. This protocol requires Alice and Bob to share a random secret key as long as the message (plaintext\index{Plaintext}) being communicated between them. The two bit-strings undergo bit-wise XOR operations to form the ciphertext\index{Ciphertext}. Mathematically,\index{One-time pad}
\begin{align}
c = s \oplus k,
\end{align}
where $\oplus$ is the bitwise XOR operation (equivalently addition modulo 2), and $c$, $s$ and $k$ are the ciphertext, plaintext and key bit-strings respectively, all of which are of the same length,
\begin{align}
	|c|=|s|=|k|.
\end{align}

@@

Importantly, the secrecy of the one-time pad\index{One-time pad} strictly requires that a key never be reused. A fresh key must be generated for each message sent, otherwise trivial frequency analysis\index{Frequency analysis} techniques can be employed to compromise security. If the same key $k$ is used to encode two messages $s_1$ and $s_2$, yielding ciphertexts,
\begin{align}
c_1&=s_1\oplus k,\nonumber\\
c_2&=s_2\oplus k,
\end{align}
then we trivially obtain,
\begin{align}
c_1 \oplus c_2 &= (s_1 \oplus k) \oplus (s_2 \oplus k) \nonumber \\
&= (s_1 \oplus s_2) \oplus (k \oplus k) \nonumber \\
&= s_1 \oplus s_2,
\end{align}
which is independent of the key. Now a frequency analysis on the bitwise XOR of two plaintexts can be applied, without requiring any knowledge of the key whatsoever.

@@

RSA \cite{bib:RSA} was the first published public-key cryptographic protocol, and forms the backbone for most encryption used on the internet today. It achieves its security based on the belief that factorising large integers into constituent primes is a computationally hard problem -- a so-called `trapdoor function'\index{Trapdoor functions}. The algorithm is built upon number theory using modular arithmetic, described in detail in Alg.~\ref{alg:RSA}.

@@

In the case of RSA encryption, whose security derives from the believed computational hardness of factorising large numbers, the most efficient known classical algorithm for integer factorisation is the general number field sieve (GNFS)\index{General number field sieve}, with time-complexity,
\begin{align} \label{eq:GNFS_scaling}
	O(\mathrm{exp}[O(1) (\log n)^{\frac{1}{3}} (\log\log n)^{\frac{2}{3}}]),
\end{align}
which scales poorly for large $n$, keeping in mind that present-day implementations of RSA accommodate key lengths of up to 4,096 bits, as for example is implemented by the Pretty Good Privacy (PGP)\index{Pretty Good Privacy (PGP)} package.

@@

Note that when performing a brute-force attack against a private encryption key\index{Private-key cryptography}, a quadratic speedup effectively halves the key length in terms of algorithmic runtime, since \mbox{$O(\sqrt{2^k}) = O(2^{k/2})$}. Thus, in the quantum era private key lengths will need to be doubled to maintain the same security against brute-force attacks.

@@

Hashing does not have any known quantum algorithm with exponential improvement, however using a Grover search\index{Grover's algorithm} one can achieve a quadratic speedup, using the same idea as for enhancing \textbf{NP}-complete problems by treating the hash function as a search oracle\index{Oracles}. This however does not pose a fundamental security concern as it will speed up the Bitcoin mining process, but does not circumvent the upper-bound on the number of coins that may be in existence. Already classical mining has pushed the Bitcoin money supply close to its asymptotic maximum and there is limited room for additional mining\footnote{Bitcoin mining has gained so much traction and become so competitive that desktop PCs have become uneconomical for mining. Instead miners are resorting to utilising specialised hardware in the form of CUDA cores\index{CUDA cores}, FPGAs\index{FPGA} and ASICs\index{ASIC} (or by secretly using the company supercomputer while the boss isn't looking).}.

@@

Thankfully, there are two saving graces. First of all, much research is being carried out into \textit{post-quantum classical cryptography}\index{Post-quantum classical cryptography}. That is, public-key cryptosystems based upon trapdoor functions\index{Trapdoor functions} that reside outside of \textbf{BQP} and are therefore not efficiently attacked by quantum computers. One such line of research is to construct cryptosystems based upon \textbf{NP}-complete problems, such as the McEliece protocol\index{McEliece protocol}. Recall from Fig.~\ref{fig:complexity_classes} that \textbf{NP}-complete is strongly believed to reside completely outside of \textbf{BQP}. However, while many computer scientists might be comfortable with such a level of security, it is nonetheless based on the unproven conjecture that \textbf{NP}-complete and \textbf{BQP} do not intersect, i.e \mbox{$\mathbf{NP}\nsubseteq\mathbf{BQP}$}. What would be much more satisfying would be protocols demonstrating information-theoretic security\index{Information-theoretic security} rather than computational security\index{Computational security}. Here quantum mechanics can help us -- \textit{quantum cryptography}.

@@

\subsection{Quantum key distribution} \label{sec:QKD} \index{Quantum key distribution (QKD)}

@@

Quantum key distribution (QKD) protocols facilitate shared, secret randomness, where any intercept-resend\index{Intercept-resend attack} (or man-in-the-middle attack) attack may be detected and rejected, guaranteed by the laws of quantum physics (specifically the Heisenberg uncertainty principle\index{Heisenberg uncertainty principle} and no-cloning theorem\index{No-cloning theorem}). This shared, secret randomness may subsequently be employed in a one-time pad cipher\index{One-time pad}, presenting us with true information-theoretic security\index{Information-theoretic security}.

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function BB84():
\begin{enumerate}
\item Alice chooses a random bit, $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{BB84\index{BB84 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string for use in a one-time pad cipher\index{One-time pad}.}\label{alg:bb84}
\end{table}

@@

To understand the secrecy of the protocol as described in Alg.~\ref{alg:bb84}, suppose an eavesdropper, Eve, were to perform an intercept-resend\index{Intercept-resend attack} attack on the channel between Alice and Bob. At that stage in the protocol Alice had not yet announced her choice of encoding bases, and Eve will not know the bases in which to measure states without randomly collapsing them onto values inconsistent with Alice's encoding. Thus, by sacrificing some of their shared bits, via openly communicating them to one another for comparison, such an attack will be detected with asymptotically high security. Now Alice and Bob have great confidence that they have a shared, secret, random bit-string, which may subsequently be employed in a one-time pad\index{One-time pad} with perfect secrecy.

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function E91():
\begin{enumerate}
\item A central server shares a Bell pair between Alice and Bob,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
\item Alice randomly measures her qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Bob randomly measures his qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Alice and Bob share what their measurement bases were (classically and unencrypted).
\item When Alice and Bob's bases were consistent they store the measurement outcomes as a shared random bit.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{E91\index{E91 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photonic Bell pairs. Upon completion of the protocol, Alice and Bob share a random bit-string of ruse in a one-time pad cipher\index{One-time pad}.}\label{alg:e91}
\end{table}

@@

Like quantum computing, QKD protocols may be adapted to the CV domain also. Alg.~\ref{alg:cv_qkd} describes a simple such scheme based on encoding in phase-space\index{Phase-space}, where the basis states are coherent states of different amplitudes and phases. The goal is the same as BB84 -- to securely share a random bit-string for use in a one-time-pad\index{One-time pad}.

### 2018-08-08 Sections/economics_of_the_quantum_internet.tex
Finito index

This effectively implies that some users pay more for computation (in terms of return on investment\index{Return on investment}) than others. While the objective cost of computation is conceptually simple to model (as performed in a rudimentary fashion in Sec.~\ref{sec:cost_of_comp}), the subjective cost is a highly non-trivial one. It will depend heavily on the scaling function of the algorithm run by a user, and of course the economic objectives of their computation -- a quantum simulation algorithm executed by an R\&D lab\index{R\&D} is likely to be of greater monetary value than and undergrad using his university's resources for completing an assignment!

@@

What is likely to arise is that most owners of quantum hardware will not be consumers, but rather investors, who float their resources on the quantum stock market, betting on changes in demand for computation and their associated subjective cost. This trading could involve transactions in the direct underlying asset, future contracts (Sec.~\ref{sec:for_contr}) for locking in required computational power at future points in time, or more complex derivatives. For example, an investor anticipating a surge in high-value computations is likely to invest more heavily into hardware with the expectation of an uptrend in market rates. And their return on investment\index{Return on investment} will reflect these market dynamics.

>>>>

This effectively implies that some users pay more for computation (in terms of return on investment\index{Return on investment (RoI)}) than others. While the objective cost of computation is conceptually simple to model (as performed in a rudimentary fashion in Sec.~\ref{sec:cost_of_comp}), the subjective cost is a highly non-trivial one. It will depend heavily on the scaling function of the algorithm run by a user, and of course the economic objectives of their computation -- a quantum simulation algorithm executed by an R\&D lab\index{R\&D} is likely to be of greater monetary value than and undergrad using his university's resources for completing an assignment!

@@

What is likely to arise is that most owners of quantum hardware will not be consumers, but rather investors, who float their resources on the quantum stock market, betting on changes in demand for computation and their associated subjective cost. This trading could involve transactions in the direct underlying asset, future contracts (Sec.~\ref{sec:for_contr}) for locking in required computational power at future points in time, or more complex derivatives. For example, an investor anticipating a surge in high-value computations is likely to invest more heavily into hardware with the expectation of an uptrend in market rates. And their return on investment\index{Return on investment (RoI)} will reflect these market dynamics.
